Best Practices for Developing Monte Carlo Methodologies in Molecular Simulations [Article v\versionnumber]

### 2025-07-15 paper/paperv1.0.tex
Added acknowledgement
Editorial comments and releases folder. Awaiting doi, etc for v1.0 publication.

% for a code block
\usepackage{listings}
\usepackage{color}
%\usepackage{hyperref}
\renewcommand{\lstlistingname}{Code Block}% Listing -> Algorithm
%\renewcommand{\lstlistingname}{Simulation}% Listing -> Algorithm
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
%\lstset{frame=tb, % horizontal lines
%\lstset{frame=none,
%\renewcommand{\familydefault}{\sfdefault}
\lstset{frame=tblr,
  language=Python,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  columns=flexible,
  basicstyle={\footnotesize\sffamily},
  %basicstyle={\small\sffamily},
  %basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=false,
  tabsize=3
}

@@

This article was funded by NIST and is not subject to U.S. Copyright.
Certain commercial firms and trade names are identified in order to specify the usage procedures adequately for reproducibility.
Such identification is not intended to imply recommendation or endorsement by the National Institute of Standards and Technology, nor is it intended to imply that related products are necessarily the best available for the purpose.

>>>>

% for a code block
\usepackage{listings}
\usepackage{color}
%\usepackage{hyperref}
\renewcommand{\lstlistingname}{Code Block}% Listing -> Algorithm
%\renewcommand{\lstlistingname}{Simulation}% Listing -> Algorithm
\definecolor{dkgreen}{rgb}{0,0.6,0}
\definecolor{gray}{rgb}{0.5,0.5,0.5}
\definecolor{mauve}{rgb}{0.58,0,0.82}
%\lstset{frame=tb, % horizontal lines
%\lstset{frame=none,
%\renewcommand{\familydefault}{\sfdefault}
\lstset{frame=tblr,
  language=Python,
  aboveskip=3mm,
  belowskip=3mm,
  showstringspaces=false,
  %columns=flexible,
  columns=fullflexible,
  basicstyle={\footnotesize\sffamily},
  %basicstyle={\small\sffamily},
  %basicstyle={\small\ttfamily},
  numbers=none,
  numberstyle=\tiny\color{gray},
  keywordstyle=\color{blue},
  commentstyle=\color{dkgreen},
  stringstyle=\color{mauve},
  breaklines=true,
  breakatwhitespace=false,
  tabsize=3
}

@@

This article was funded by NIST and is not subject to U.S. Copyright.
Certain commercial firms and trade names are identified in order to specify the usage procedures adequately for reproducibility.
Such identification is not intended to imply recommendation or endorsement by the National Institute of Standards and Technology, nor is it intended to imply that related products are necessarily the best available for the purpose.
Support to D.A.K. from the National Science Foundation (CBET-2152946) and the Schmid Family Foundation is gratefully acknowledged.
